Simulating High-Dimensional Multivariate Data

### 2021-03-01 030-bigsimr-package.Rmd
Revise 030 prior to CSDA submission

This section describes a low-dimensional (2D) random vector simulation workflow via the `bigsimr` `R` package (https://github.com/SchisslerGroup/r-bigsimr).
`bigsimr` provides an interface to the native code written in Julia, registered as the `Bigsimr` Julia package (https://github.com/adknudson/Bigsimr.jl).
In addition to the native Julia `Bigsimr` package and `R` interface `bigsimr`, we also provide a python interface `bigsimr` (https://github.com/SchisslerGroup/python-bigsimr/) that interfaces with the Julia `Bigsimr` package. 
The Julia implementation provides a high-performance implementation of our proposed random vector generation algorithm and associated functions (see Section \@ref(algorithms)).
When designing `bigsimr`, we aimed to conveniently provide parallelized computation, through multi-core and GPU acceleration, while allowing advanced users to customize.

@@

The bounds on the Pearson correlation coefficient $R_P$ between these margins is restricted as seen below in our MC estimated correlation bounds:

>>>>

This section describes a low-dimensional (2D) random vector simulation workflow via the `bigsimr` `R` package (https://github.com/SchisslerGroup/r-bigsimr).
The package `bigsimr` provides an interface to the native code written in Julia, registered as the `Bigsimr` Julia package (https://github.com/adknudson/Bigsimr.jl).
In addition to the native Julia `Bigsimr` package and `R` interface `bigsimr`, we also provide a python interface `bigsimr` (https://github.com/SchisslerGroup/python-bigsimr/) that interfaces with the Julia `Bigsimr` package. 
The Julia implementation provides a high-performance implementation of our proposed random vector generation algorithm and associated functions (see Section \@ref(algorithms)).
When designing `bigsimr`, we aimed to conveniently provide parallelized computation, through multi-core and GPU acceleration, while allowing advanced users to customize.

@@

The bounds on the Pearson correlation coefficient $R_P$ between these margins are restricted as seen below in our MC estimated correlation bounds:
